Inpainting with dimensionality reduction in the Fourier domain

### 2011-06-17 project/Paper/paper.tex
+ Started work on gradient descent description

\subsection{Offline parameter estimation}

>>>>

\subsection{Offline parameter estimation}
As shown in table \ref{parameters}, there are a total of 10 parameters in our algorithm that can be set.
For many of them, it is quite clear what values should be used. For example, the size of the gauss kernel
should be a bit larger than the biggest assumed hole in the image. For others, like the maximum number of
iterations, it is not so clear. And yet others have a clear speed / accuracy tradeoff, like the stopping
conditions of the online threshold estimation.

Because we thought it not feasable to tune all the parameters by hand, we wrote a program to
do the offline parameter estimation. The idea is to do this once for a few representative images, and get
parameters that can model as closely as possible many of the images we are interested in.
Our proposed method combines a gradient descent method with ideas from cross-validation, and tunes our
10-dimensional parameter-space, maximising time and accuracy.

\subsubsection{Error function}

\subsubsection{Gradient descent}
